The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S.

### 2023-02-22 outputs/paper/paper.qmd
Revised and merged

birth1 %>% 
ggplot(mapping = aes(x = year, y = birthrate, color = agegroup)) + 
  geom_line()  +
  labs(
    title = "Trends in Birth Rates by Age Group",
    x = "Year",
    y = "birthrate",
    caption = "Source: CDC Vital Statistics Births Reports.",
    color = "Age Group"
  ) +
  scale_x_continuous(limits=c(1991, 2020), breaks=seq(1991, 2020, by = 8)) +
  scale_y_continuous(limits = c(0,125), breaks = seq(0,125, by=20)) +
  theme_light()
```
@fig-5 shows lots of important information about when people tend to have kids at certain age over the timeframe from 1990 to 2020. Based on the graph, the data shows that more people are having kids after the age 30 during this present time. In the past, most people tend to have kids before the age 30. Around the years 2000 to 2005, that is when the lifestyle started to change where people tend to either get marry later, or have kids later which is why the trend of birth rates in age 30 and up are going higher from the 2000's. While, the births before the age of 30 tends to slow down and decreasing over time from the 2000's. According to the graph, maybe in another 100 years, we can expect that most birth rates can happen around the age 40-44.

@@

## Weakness and Next steps

@@

### Causes and Impacts of Declining Birth Rates

### Age

>>>>

birth1 %>% 
ggplot(mapping = aes(x = year, y = birthrate, color = agegroup)) + 
  geom_line()  +
  labs(
    title = "Trends in Birth Rates by Age Group",
    x = "Year",
    y = "birthrate",
    caption = "Source: CDC Vital Statistics Births Reports.",
    color = "Age Group"
  ) +
  scale_x_continuous(limits=c(1991, 2020), breaks=seq(1991, 2020, by = 8)) +
  scale_y_continuous(limits = c(0,125), breaks = seq(0,125, by=20)) +
  theme_light()
```

@fig-5 shows lots of important information about when people tend to have kids at certain age over the timeframe from 1990 to 2020. Based on the graph, the data shows that more people are having kids after the age 30 during this present time. In the past, most people tend to have kids before the age 30. Around the years 2000 to 2005, that is when the lifestyle started to change where people tend to either get marry later, or have kids later which is why the trend of birth rates in age 30 and up are going higher from the 2000's. While, the births before the age of 30 tends to slow down and decreasing over time from the 2000's. According to the graph, maybe in another 100 years, we can expect that most birth rates can happen around the age 40-44.

@@

## Weakness and Moviforward

@@

### Movingforward
